Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-25 data_appendix.Rmd
data appendix trying to get the variables saved in the processed data folder

Create a bullet list with the name of each variable in the dataset followed by any information the user would need to understand it.

@@

*This section should include a discussion of the processing and merging steps needed to create your basic data. The code to implement these steps should be included in chunks in this section. Once the final merged data has been created, you should use the dfSummary function again to summarize the data you will be using. You should also save a file containing all the objects you will use in your final analysis to the processed_data folder.*

@@

total_2005 <- readRDS(file = analysis_variables.rds")

@@

At the end of the section, you should save all of these variables in the processed_data folder of your repository.

>>>>

@@

@@

setwd(dir = "C:/Users/katya/Documents/MyDocuments/A Smith College Spring Semester/Natural Resource Economics/seminar-paper-katyagi21/processed_data/")

total_2005 <- readRDS(file = "analysis_variables.rds")

@@
